Response to reviewers

### 2022-02-16 paper/paper-jsdse/paper-jsdse.tex
Add all of the reviewers' comments in the response file, add some of the response as well.

This paper demonstrates the steps of cleaning data, including subjective decisions made on dealing with anomalies, and documents the process, as recommended by Huebner, Vach, and Cessie (2016). They emphasize that making the data cleaning process accountable and transparent is imperative and essential for the integrity of downstream statistical analyses and model building. Clean data often then goes through an ``initial data analysis'' (IDA) (Chatfield 1985), where one would summarize and scrutinize the data, especially to check if the data is consistent with assumptions required for modeling. This stage is related to exploratory data analysis (EDA), coined by Tukey (1977) with a focus on learning from data. EDA can be considered to encompass IDA. In practice the three stages of cleaning, summarizing and exploring are cyclical, that one often needs to do more cleaning after scrutinizing. Dasu and Johnson (2003) say that data cleaning and exploration is a difficult task and typically consumes a large percentage of the time spent in analyzing data.

@@

According to Wickham (2014), tidy data sets comply with three rules: (i) each variable forms a column, (ii) each observation forms a row, and (iii) each type of observational unit forms a table. The raw data, \texttt{new\_data\_qnames}, does not comply with these rules as it is organised such that each row corresponds to an individual. As respondents can have multiple jobs at specific years, the column names, such as \texttt{HRP1\_1979}, \texttt{HRP2\_1979}, \texttt{HRP1\_1980} and \texttt{HRP2\_1980}, contain the information about the job number up to 5 (\texttt{HRP1} = job 1, \texttt{HRP2} = job 2) and the year. The raw data consequently has a large number of columns (663 to be specific). The values in the cell under the variables that begin with \texttt{HRP} correspond to the hourly wage in dollars. A glimpse of this data shows:

\begin{verbatim}
#> 'data.frame':    12686 obs. of  663 variables:
#>  $ CASEID_1979                               : int  1 2 3 4 5 6 7 8 ...
#>  $ HRP1_1979                                 : int  328 385 365 NA 310 NA NA NA ...
#>  $ HRP2_1979                                 : int  NA NA NA NA 375 NA NA NA ...
#>  $ HRP3_1979                                 : int  NA NA 275 NA NA NA NA NA ...
#>  $ HRP4_1979                                 : int  NA NA NA NA NA 250 NA NA ...
#>  $ HRP5_1979                                 : int  NA NA NA NA NA NA NA NA ...
#>  $ HRP1_1980                                 : int  NA 457 397 NA 333 275 300 394 ...
#>  $ HRP2_1980                                 : int  NA NA 367 NA NA NA NA NA ...
#>  $ HRP3_1980                                 : int  NA NA 380 NA NA NA 290 NA ...
#>  $ HRP4_1980                                 : int  NA NA NA NA NA NA NA NA ...
#>   [list output truncated]
\end{verbatim}

>>>>

This paper demonstrates the steps of cleaning data, including subjective decisions made on dealing with anomalies, and documents the process, as recommended by Huebner, Vach, and Cessie (2016). They emphasize that making the data cleaning process accountable and transparent is imperative and essential for the integrity of downstream statistical analyses and model building. Clean data often then goes through an ``initial data analysis'' (IDA) (Chatfield 1985), where one would summarize and scrutinize the data, especially to check if the data is consistent with assumptions required for modeling. This stage is related to exploratory data analysis (EDA), coined by Tukey (1977) with a focus on learning from data. EDA can be considered to encompass IDA. In practice, the three stages of cleaning, summarizing, and exploring are cyclical, that one often needs to do more cleaning after scrutinizing. Dasu and Johnson (2003) say that data cleaning and exploration is a difficult task and typically consumes a large percentage of the time spent in analyzing data.

@@

According to Wickham (2014), tidy data sets comply with three rules: (i) each variable forms a column, (ii) each observation forms a row, and (iii) each type of observational unit forms a table. The raw data, \texttt{new\_data\_qnames}, does not comply with these rules as it is organised such that each row corresponds to an individual. As respondents can have multiple jobs at specific years, the column names, such as \texttt{HRP1\_1979}, \texttt{HRP2\_1979}, \texttt{HRP1\_1980} and \texttt{HRP2\_1980}, contain the information about the job number up to 5 (\texttt{HRP1} = job 1, \texttt{HRP2} = job 2) and the year. The raw data consequently has a large number of columns (742 to be specific). The values in the cell under the variables that begin with \texttt{HRP} correspond to the hourly wage in dollars. A glimpse of this data shows:

\begin{verbatim}
#> 'data.frame':    12686 obs. of  742 variables:
#>  $ CASEID_1979                               : int  1 2 3 4 5 6 7 8 ...
#>  $ HRP1_1979                                 : int  328 385 365 NA 310 NA NA NA ...
#>  $ HRP2_1979                                 : int  NA NA NA NA 375 NA NA NA ...
#>  $ HRP3_1979                                 : int  NA NA 275 NA NA NA NA NA ...
#>  $ HRP4_1979                                 : int  NA NA NA NA NA 250 NA NA ...
#>  $ HRP5_1979                                 : int  NA NA NA NA NA NA NA NA ...
#>  $ HRP1_1980                                 : int  NA 457 397 NA 333 275 300 394 ...
#>  $ HRP2_1980                                 : int  NA NA 367 NA NA NA NA NA ...
#>  $ HRP3_1980                                 : int  NA NA 380 NA NA NA 290 NA ...
#>  $ HRP4_1980                                 : int  NA NA NA NA NA NA NA NA ...
#>   [list output truncated]
\end{verbatim}

### 2022-02-16 paper/paper.Rmd
Add all of the reviewers' comments in the response file, add some of the response as well.

Statistics and data science education relies on cleaned and simplified data, suitably called textbook data, for clear examples about how to apply different techniques. An example of this, is the wages data made public by @SingerJudithD2003Alda which can be used to teach generalized linear models, in addition to hierarchical, mixed effects and multilevel. The data records hourly wages of a sample of high school dropouts, from 1979-1994, along with the demographic variables, such as education and race, taken from the National Longitudinal Survey of Youth (NLSY79) [@nlsy79].

The story from modeling the data (and as reported by Singer and Willett) is that wages increase with the length of time in the workforce, higher level of education leads to higher wages, and that race makes a difference, on average. An exploratory analysis reveals however that the individual experience varies a great deal from the overall average. Some individuals experience a decline in wages the longer they are in the workforce, and many experience volatility in their wages. The wages data was used to illustrate exploratory longitudinal data analysis in @ilk2004, and was further developed into a case study for use in the teaching of exploratory data analysis at `r censor_word("Iowa State University")`.

The story from modeling the data (and as reported by Singer and Willett) is that wages increase with the length of time in the workforce, higher level of education leads to higher wages, and that race makes a difference, on average. An exploratory analysis reveals however that the individual experience varies a great deal from the overall average. Some individuals experience a decline in wages the longer they are in the workforce, and many experience volatility in their wages.

@@

This paper demonstrates the steps of cleaning data, including subjective decisions made on dealing with anomalies, and documents the process, as recommended by @HuebnerMariannePhD2016Asat. They emphasize that making the data cleaning process accountable and transparent is imperative and essential for the integrity of downstream statistical analyses and model building. Clean data often then goes through an "initial data analysis" (IDA) [@Chatfield1985TIEo], where one would summarize and scrutinize the data, especially to check if the data is consistent with assumptions required for modeling. This stage is related to exploratory data analysis (EDA), coined by @tukey with a focus on learning from data. EDA can be considered to encompass IDA. In practice the three stages of cleaning, summarizing and exploring are cyclical, that one often needs to do more cleaning after scrutinizing. @DasuTamraparni2003Edma say that data cleaning and exploration is a difficult task and typically consumes a large percentage of the time spent in analyzing data.

@@

<!--AE comment: I was confused by the following section: “We choose to use this revised May data because it seemed to have less missing and presumably has been checked. However, there is no revised May data for 2012, 2014, 2016, and 2018, thus, we use the ordinary May data for these years.” I was assuming the data was collected on a yearly basis, but this section suggests it was collected each month. Please clarify somewhere in the paper. 
-->
The next step is tidying to obtain `hgc` and `ged`. As the highest grade completed is already exist in  `new_data_qnames` and stored in year unit (e.g., 10, 11, 12, 13, and so on), we only rename the column name to be `hgc_i` and recode it so we have the factor data type (e.g., 10th grade, 11th grade, and so on). For `ged`, we only separate the year of survey and the GED status of the individual. Later on, this variable is useful to determine the refreshed high school dropouts data.

>>>>

Statistics and data science education relies on cleaned and simplified data, suitably called textbook data, for clear examples about how to apply different techniques. An example of this, is the wages data made public by @SingerJudithD2003Alda in their book, Applied longitudinal data analysis: Modeling change and event occurrence,  which can be used to teach generalized linear models, in addition to hierarchical, mixed effects and multilevel models. The data records hourly wages of a sample of high school dropouts, from 1979-1994, along with the demographic variables, such as education and race, taken from the National Longitudinal Survey of Youth (NLSY79) [@nlsy79].

The story from modeling the data (and as reported by Singer and Willett) is that wages increase with the length of time in the workforce, higher level of education leads to higher wages, and that race makes a difference, on average. An exploratory analysis reveals, however, that the individual experience varies a great deal from the overall average. Some individuals experience a decline in wages the longer they are in the workforce, and many experience volatility in their wages. The wages data was used to illustrate exploratory longitudinal data analysis in @ilk2004, and was further developed into a case study for use in the teaching of exploratory data analysis at `r censor_word("Iowa State University")`.

<!--The story from modeling the data (and as reported by Singer and Willett) is that wages increase with the length of time in the workforce, higher level of education leads to higher wages, and that race makes a difference, on average. An exploratory analysis reveals however that the individual experience varies a great deal from the overall average. Some individuals experience a decline in wages the longer they are in the workforce, and many experience volatility in their wages. [DA: It seems that this paragraph is repetion form the previous paragraph.]-->

@@

This paper demonstrates the steps of cleaning data, including subjective decisions made on dealing with anomalies, and documents the process, as recommended by @HuebnerMariannePhD2016Asat. They emphasize that making the data cleaning process accountable and transparent is imperative and essential for the integrity of downstream statistical analyses and model building. Clean data often then goes through an "initial data analysis" (IDA) [@Chatfield1985TIEo], where one would summarize and scrutinize the data, especially to check if the data is consistent with assumptions required for modeling. This stage is related to exploratory data analysis (EDA), coined by @tukey with a focus on learning from data. EDA can be considered to encompass IDA. In practice, the three stages of cleaning, summarizing, and exploring are cyclical, that one often needs to do more cleaning after scrutinizing. @DasuTamraparni2003Edma say that data cleaning and exploration is a difficult task and typically consumes a large percentage of the time spent in analyzing data.

@@

<!--AE comment: I was confused by the following section: “We choose to use this revised May data because it seemed to have less missing and presumably has been checked. However, there is no revised May data for 2012, 2014, 2016, and 2018, thus, we use the ordinary May data for these years.” I was assuming the data was collected on a yearly basis, but this section suggests it was collected each month. Please clarify somewhere in the paper. 
-->
The next step is tidying to obtain `hgc` and `ged`. Besides that `hgc` is available in the original data, along with `ged`, it is used to subset the data to the high school dropouts as in the original data. As the highest grade completed is already exist in  `new_data_qnames` and stored in year unit (e.g., 10, 11, 12, 13, and so on), we only rename the column name to be `hgc_i` and recode it so we have the factor data type (e.g., 10th grade, 11th grade, and so on). For `ged`, we only separate the year of survey and the GED status of the individual.

### 2022-02-16 paper/paper.tex
Add all of the reviewers' comments in the response file, add some of the response as well.

Statistics and data science education relies on cleaned and simplified data, suitably called textbook data, for clear examples about how to apply different techniques. An example of this, is the wages data made public by Singer and Willett (2003) which can be used to teach generalized linear models, in addition to hierarchical, mixed effects and multilevel. The data records hourly wages of a sample of high school dropouts, from 1979-1994, along with the demographic variables, such as education and race, taken from the National Longitudinal Survey of Youth (NLSY79) (Bureau of Labor Statistics, U.S. Department of Labor 2021a).

The story from modeling the data (and as reported by Singer and Willett) is that wages increase with the length of time in the workforce, higher level of education leads to higher wages, and that race makes a difference, on average. An exploratory analysis reveals however that the individual experience varies a great deal from the overall average. Some individuals experience a decline in wages the longer they are in the workforce, and many experience volatility in their wages. The wages data was used to illustrate exploratory longitudinal data analysis in Ilk (2004), and was further developed into a case study for use in the teaching of exploratory data analysis at CENSORED.

The story from modeling the data (and as reported by Singer and Willett) is that wages increase with the length of time in the workforce, higher level of education leads to higher wages, and that race makes a difference, on average. An exploratory analysis reveals however that the individual experience varies a great deal from the overall average. Some individuals experience a decline in wages the longer they are in the workforce, and many experience volatility in their wages.

This disparity between the average and the individual is a part of statistics, as a discipline, that require more attention. This particular data set is a prime example of discussing this disparity. Textbook data sets have longevity if there is a unresolved mystery. The iris data (Andereson 1935) is a prime example. It has withstood the test of time because the three species cannot be perfectly classified, and so it continues to challenge researchers and instructors to do better in the analysis. (A side note: the iris data is best replaced today with the penguins data (Horst, Hill, and Gorman 2020), which has similar qualities, is new and does not suffer from a connection with eugenics (Stodel 2020).) We argue that the wages data is in this class of textbook data, too, because it presents a challenge for longitudinal data analysis: how can we better summarize and explain the individual experience?

>>>>

Statistics and data science education relies on cleaned and simplified data, suitably called textbook data, for clear examples about how to apply different techniques. An example of this, is the wages data made public by Singer and Willett (2003) which can be used to teach generalized linear models, in addition to hierarchical, mixed effects and multilevel models. The data records hourly wages of a sample of high school dropouts, from 1979-1994, along with the demographic variables, such as education and race, taken from the National Longitudinal Survey of Youth (NLSY79) (Bureau of Labor Statistics, U.S. Department of Labor 2021a).

The story from modeling the data (and as reported by Singer and Willett) is that wages increase with the length of time in the workforce, higher level of education leads to higher wages, and that race makes a difference, on average. An exploratory analysis reveals, however, that the individual experience varies a great deal from the overall average. Some individuals experience a decline in wages the longer they are in the workforce, and many experience volatility in their wages. The wages data was used to illustrate exploratory longitudinal data analysis in Ilk (2004), and was further developed into a case study for use in the teaching of exploratory data analysis at CENSORED.

This disparity between the average and the individual is a part of statistics, as a discipline, that require more attention. This particular data set is a prime example of discussing this disparity. Textbook data sets have longevity if there is a unresolved mystery. The iris data (Andereson 1935) is a prime example. It has withstood the test of time because the three species cannot be perfectly classified, and so it continues to challenge researchers and instructors to do better in the analysis. (A side note: the iris data is best replaced today with the penguins data (Horst, Hill, and Gorman 2020), which has similar qualities, is new and does not suffer from a connection with eugenics (Stodel 2020). We argue that the wages data is in this class of textbook data, too, because it presents a challenge for longitudinal data analysis: how can we better summarize and explain the individual experience?

### 2022-02-16 response/response1.Rmd
Add all of the reviewers' comments in the response file, add some of the response as well.

We agree that there is substantial literature on data cleaning. We have referenced one of the main works, Dasu and Johnson (2003) but don't feel it is necessary to cite more than this. We have similarly only pointed to one main reference for IDA and EDA.

@@

* We thank the reviewer for pointing out to us that the data contains information on the work experience -- this additional data is added in the extraction of the data in Figure 1. This information was compared with Singer & Willet's original data. Comparison shown in Figure 7 shows that the information does not match up, however, there is a high correlation between the variables.

@@

@@

@@

\begin{description}
\item[Reviewer 2:]\textcolor{violet}{I think there is a narrative step missing here, which is that looking at those samples led you to look at plots that show values for the wage variable over all participants and all years. The phrase “the summary plots” was not enough description for me to know what to expect when I flipped to Figure 3. Please be explicit about what the three plots were, why they were made, and what you were looking for. I think there is another narrative step missing about Figure 3C, which is that after you saw there were outliers you tried to identify which respondents had the extreme values. Again, please spell this out in the text. When you return to the plots for the entire dataset in Figure 5, please make parallel comments.}
\end{description}
* **NEED HELP**

@@

\begin{description}
\item[Reviewer 2:]\textcolor{violet}{
What does “It implies that the fluctuation can still be observed in the data after the treatment.” mean? I suspect this sentence should be replaced with something along the lines of “The figure shows that fluctuations in wages still exist even in the imputed data.”}
\end{description}

@@

* We removed this sentence as we already have the `yr_wforce` variable which is calculated from the year of the individual start working.

@@

>>>>

* We agree that there is substantial literature on data cleaning. We have referenced one of the main works, Dasu and Johnson (2003) but don't feel it is necessary to cite more than this. We have similarly only pointed to one main reference for IDA and EDA.

@@

* We thank the reviewer for pointing out to us that the data contains information on the work experience -- this additional data is added in the extraction of the data in Figure 1. We also add a Subsection dedicated to explain this variable, i.e., Subsection 3.2. Calculated variables: work experience. This information was compared with Singer & Willet's original data. Comparison shown in Figure 7 shows that the information does not match up, however, there is a high correlation between the variables.

@@

* Sometimes, the natural log is used to rescale the variable in the graph to adjust with the skewness in the data. Singer and Willet (2003) use the natural log to store the wages data by default, although without mention their motivation of doing so. Thus, we also use the natural log in Figure 8 to compare the refreshed data with the original data.

@@

* We have mentioned the book's title in the Introduction. The motivation of refreshing this text book data and how it is used for teaching purpose are discussed in the Introduction of the paper.

@@

\begin{description}
\item[Reviewer 2:]\textcolor{violet}{I think there is a narrative step missing here, which is that looking at those samples led you to look at plots that show values for the wage variable over all participants and all years. The phrase “the summary plots” was not enough description for me to know what to expect when I flipped to Figure 3. Please be explicit about what the three plots were, why they were made, and what you were looking for. I think there is another narrative step missing about Figure 3C, which is that after you saw there were outliers you tried to identify which respondents had the extreme values. Again, please spell this out in the text. When you return to the plots for the entire dataset in Figure 5, please make parallel comments.}
\end{description}

@@

\begin{description}
\item[Reviewer 2:]\textcolor{violet}{What does “It implies that the fluctuation can still be observed in the data after the treatment.” mean? I suspect this sentence should be replaced with something along the lines of “The figure shows that fluctuations in wages still exist even in the imputed data.”}
\end{description}

@@

* We removed this sentence as we already have the `stwork` and `yr_wforce`  variables which are the year of individual start working and length of the years of individual entering the labor force, respectively.

@@

\begin{description}
\item[Reviewer 3:]\textcolor{violet}{Where is IDA undervalued and neglected? Research? Teaching? Both?}
\end{description}

* We removed this sentences, and edited the explanation about IDA in Paragraph 6 of the Introduction.

\begin{description}
\item[Reviewer 3:]\textcolor{violet}{The authors discuss refreshing an example from Singer and Willet (2003), but this isn’t ever completed. They compare the data, but not the longitudinal model. Again, it’s more about demonstrating a procedure for “initial data analysis” than it is reproducing Singer and Willet (2003).}
\end{description}

* Our main aim in this paper is to refresh the data, which is used as one of examples of longitudinal data and its modelling in Singer and Willet (2003). In other words, we only aims to refresh the data  until the most recent survey period, and not the longitudinal model, so that it is more relevant for today's context, especially, if its is used for teaching.

\begin{description}
\item[Reviewer 3:]\textcolor{violet}{Tidy and tame data are discussed in passing and the utility of tidy and tame data are not obvious. The authors later describe tidy data rather clearly (page 7) but tame data never receives the same treatment.}
\end{description}

* We put explanation on the difference between tidy and tame data in the Introduction (Paragraph 7). Tame data is sort of a result product, in which, in order to produce it, we need to tidy the data.

\begin{description}
\item[Reviewer 3:]\textcolor{violet}{A historical context of NLSY79 would be helpful. Specifically, the dropped subjects are mentioned but there’s no context of why. By the argument of the paper, these steps should be transparent and well-considered.}
\end{description}

* We have added the reason of why some subject were dropped from the interview in Section 2.1.

\begin{description}
\item[Reviewer 3:]\textcolor{violet}{The author switches between gender (man/woman/etc) and sex (male/female/etc.) throughout the manuscript. Further, the explanation here covers important ideas in teaching how to use data on gender/sex and race, but it’s just the beginning of ideas. It might be better to discuss the questions on the survey and discuss possible shortcomings, rather than make a somewhat empty gesture towards today’s standard.}
\end{description}

\begin{description}
\item[Reviewer 3:]\textcolor{violet}{The discussion around highest grade completed is mechanical in what was done, but lacks substantive reasoning for those decisions and possible downstream consequences.}
\end{description}

* The variable of `highest grade completed`, besides it is available in the original data, it is also use to filter the high school dropouts (the subset of NLSY79 cohort that is contained in the original data). We explain how we use this variable, along with a newly added variable, GED, and possible downstream consequences in Subsection 4.1 Filtering: Determining who is a dropout.

\begin{description}
\item[Reviewer 3:]\textcolor{violet}{It appears the goal of the paper switches to just IDA and dealing with problematic points here. This is completed in the paper.} 
\end{description}

\begin{description}
\item[Reviewer 3:]\textcolor{violet}{Gender (man/woman/etc). Sex (male/female/etc).} 
\end{description}

\begin{description}
\item[Reviewer 3:]\textcolor{violet}{It is not clear why participants without a high school degree are not part of the analysis.} 
\end{description}

* In the current version of the manuscript, we have included all of the cohort, regardless of their school degree in a dataset called `wages`. However, we also subset the data to be high school dropouts only as we aims to refresh Singer and Willet's data (only contains male high school dropouts aged 14-17 years old when first interviewed). Hence, for comparability, we only analyse the high school dropouts in Section 4.

\begin{description}
\item[Reviewer 3:]\textcolor{violet}{Figure 2 is helpful for observing the data there is a lot of variability in both hourly wage and trends. A discussion about censored data might be helpful here – this is not something you impute from the data.} 
\end{description}

\begin{description}
\item[Reviewer 3:]\textcolor{violet}{You’re using iteratively reweighted least squares with Huber weighting.} 
\end{description}

\begin{description}
\item[Reviewer 3:]\textcolor{violet}{I’m not sure this is accurate. The robustlmm package in R fits these models rather quickly with thousands of observations. What are the authors using? Does it run out of memory (requires more RAM) or does it take too much time?}
\end{description}

* We use `MASS` package instead of `robustlmm` package. We have tried to use `robustlmm`, but perhaps because the data is large and imbalanced, the model was not converging. Also, for reproducibility reason, we made it more affordable (in terms of memory and time), especially when people want to perform the stages in cleaning the data in class/teaching.

\begin{description}
\item[Reviewer 3:]\textcolor{violet}{The choice of 0.12 seems arbitrary at best. I don’t see any justification for this approach (e.g., literature, simulations, etc). Why not use bi-square, instead of huber, and simply impute for observations with weight 0. While still arbitrary, it’s decided by the bisquare model and isn’t a guesstimate. Further, it would be sensible for any dataset and not just this one. (This would correspond to a smaller threshold, which may catch too many strange outcomes). In any case, it’s hard to justify something so adhoc.}
\end{description}

\begin{description}
\item[Reviewer 3:]\textcolor{violet}{It’s unclear about what fluctuation or treatment the author is referring to.}
\end{description}

* Fluctuation is the variability in the data (up and down in the wages), while treatment is imputing the extremely high wages (anomaly) with their RLM's predicted value. The detail explanation of fluctation is discussed in Subsection 3.3 Initial Data Analysis, while the treatment is explained in Subsection 3.4 (Paragraph 3).

\begin{description}
\item[Reviewer 3:]\textcolor{violet}{If the goal was to reproduce the textbook data, then why weren’t wages inflation-adjusted?}
\end{description}

* This is not done for the refreshed data because we plan to keep refreshing it as the data from the newest survey period  release. Thus, the 1990 prices might not be relevant anymore for the future context. Hence, we keep it as the original value to allow the users to treat it as their needs. In other words, the inflation-adjustment of the wages is better to do with each wave of new data added, so that it is relative to the last date in the data.

* This explanation exists in the manuscript in Section 4.2 and Section 5.

\begin{description}
\item[Reviewer 3:]\textcolor{violet}{Figure 7 (Figure 8 in the current manuscript) is interesting, but it wasn’t until my second time through that I realized this was the textbook example for replicating. There is a clear difference in analyses (different question really), but is there anything to justify a similarity, or improvement of the analysis?}
\end{description}

\begin{description}
\item[Reviewer 3:]\textcolor{violet}{(page 14, line 46) Thank you for this acknowledgment. I think this is true for most analyses. It doesn’t mean that you shouldn’t transparently and fully investigate your own choices.}
\end{description}
